Simulating High-Dimensional Multivariate Data

### 2021-02-24 010-background.Rmd
Revise 3 example genes code and scatterplot mat

```{r ch010-realDataTab}
set.seed(01122021)
num_genes    <- 3
num_patients <- 5
gene_sample  <- sample(example_genes, num_genes)

@@

```{r ch010-realDataFig, cache=FALSE, fig.width=8, fig.cap="Marginal scatterplots, densities, and estimated pairwise Spearman's correlations for three example genes from Table 1. The data possess heavy-right tails, are discrete, and have non-trivial intergene correlations. Modeling these data motivate our simulation methodology."}
GGally::ggpairs(
  data = small_brca[,-1],
  upper = list(continuous = GGally::wrap('cor', method = "spearman"))
) + theme_bw()
```

>>>>

```{r ch010-realDataTab}
set.seed(02242021)
num_genes    <- 3
num_patients <- 5
gene_sample  <- sample(example_genes, num_genes)

@@

```{r ch010-realDataFig, cache=FALSE, fig.width=8, fig.cap="Marginal scatterplots, densities, and estimated pairwise Spearman's correlations for three example genes from Table 1. The data possess heavy-right tails, are discrete, and have non-trivial intergene correlations. Modeling these data motivate our simulation methodology."}
GGally::ggpairs(
  data = example_brca[, gene_sample],
  upper = list(continuous = GGally::wrap('cor', method = "spearman"))
) + theme_bw()
```
